Pre-/Post-Trikafta in CFRD

### 2022-02-02 Christine Chan/Pre-post Trikafta/pre_post_trikafta_merge.Rmd

# add in a site id variable
montana_long$site = "Montana"
#########################

@@

>>>>

#hba1c should be a numeric, one with a note : pre trikafta cffid 1433411
montana_long = montana_long %>% rename(HbA1c_original = HbA1c)
montana_long = montana_long %>% mutate(hba1c_spc = str_detect(HbA1c_original, " "),
                               HbA1c = as.numeric(ifelse(hba1c_spc,sub(" .*", "", montana_long$HbA1c_original), HbA1c_original)))

montana_long = montana_long %>% select(-c(hba1c_spc, HbA1c_original))
# add in a site id variable
montana_long$site = "Montana"
#########################

@@

```{r analysis dataset}
# full join long datasets
analysis_data = full_join(chco_long, montana_long)
analysis_data = full_join(analysis_data, uw_long)

# export csv analysis_data
write.csv(analysis_data, file = "S:/Vigers/CF/Christine Chan/Prepost Triakfta/Data_Cleaned/analysis_data.csv")
```
